Parsing Postfix log files

### 2008-10-28 doc/logparser-architecture.tex
Corrections to section 4: mainly just a big bunch of TODO items.

\subsection{Parser design}

@@

It should be clear from the earlier Postfix background (\sectionref{postfix
background}) that log files produced by Postfix are not fixed; they vary
widely from host to host, depending on the set of restrictions chosen by
the administrator.  With this in mind, one of the parser's design aims was
to make adding new rules as easy as possible, to enable administrators to
properly parse their log files.  To enable this the parser is divided into
three parts:

@@

It may help to think of the rules and actions as components that plug into
the framework.

@@

XXX MERGE THE NEXT TWO PARAGRAPHS\@.

@@

\subsection{Rule characteristics}

@@

\subsection{Overlapping rules}

@@

@@

XXX TO BE WRITTEN\@.

XXX TO BE WRITTEN\@.

>>>>

XXX NEEDS AN INTRODUCTION ONCE CONTENT HAS SETTLED\@.

XXX MERGE SOME OF THE PAPER'S CONTENT IN HERE\@.

\subsection{Parser architecture and design}

@@

It should be clear from the earlier Postfix background (\sectionref{postfix
background}) that log files produced by Postfix vary widely from host to
host, depending on the set of restrictions chosen by the administrator.
With this in mind, one of the parser's design aims was to make adding new
rules as easy as possible, to enable administrators to properly parse their
own log files.  To enable this the architecture is divided into three
parts:

XXX UPDATE SECTION REFERENCES BELOW\@: THEY NEED TO REFER TO BOTH THE
ARCHITECTURE AND THE IMPLEMENTATION\@.

@@

It may help to think of the rules and actions as components that plug into
the framework.  The framework tries each rule in turn until is finds one
which matches the log line, then invokes the action specified by the rule.

@@

XXX MERGE THE NEXT TWO PARAGRAPHS\@.  PULL CONTENT FROM THE PAPER\@.

@@

XXX TO BE WRITTEN\@.  TAKE CONTENT FROM THE PAPER AND POSSIBLY FROM THE
IMPLEMENTATION SECTION\@.

\subsubsection{Rule characteristics}

@@

\subsubsection{Overlapping rules}

@@

XXX PULL CONTENT FROM THE PAPER FOR HERE\@; IT'S BETTER WRITTEN\@.

@@

XXX TO BE WRITTEN\@.  START WITH THE CONTENT FROM THE PAPER, THEN CHECK THE
IMPLEMENTATION SECTION\@.
